Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-01-29 glsb.tex
add new malin 1 paper
writing

\documentclass[12pt,preprint]{aastex}
%\documentclass{emulateapj}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{xspace}
\def\arcsec{$^{\prime\prime}$}
\bibliographystyle{apj}
\newcommand\degree{{^\circ}}
\newcommand\surfb{$\mathrm{mag}/\square$\arcsec}
\newcommand\Gyr{\rm{~Gyr}}
\newcommand\msun{\rm{M}_\odot}
\newcommand\kms{km s$^{-1}$}
\newcommand\al{$\alpha$}
\newcommand\ha{$\rm{H}\alpha$}
\newcommand\hb{$\rm{H}\beta$}
\newcommand\HI{\ion{H}{1}}

@@

@@

\begin{deluxetable}{l l c c c c c c}
%\tabletypesize{\small \footnotesize \scriptsize}
\tabletypesize{\small}
%\rotate
\tablewidth{0pt}
%\tablenum{num}
%\tablecolumns{num}
%\tableheadfrac{num}
\tablecaption{Basic Properties of GLSB Galaxies}
\tablehead{
\colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
& \colhead{$\sigma$} & Stellar Mass & \colhead{\HI\ mass}\\
     &  \colhead{(DR 9)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms}  &\colhead{log$_{10}$M$_{\odot}$}&\colhead{log$_{10}$M$_{\odot}$}
\label{basic_prop}}    
\startdata
Malin 2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  & 11.15 & 10.6\\
UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 & 10.66 & 10.5
\enddata
\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS.}
\end{deluxetable}

@@

The diameters of GLSB disks are very large, with Malin~1's stellar dist detected out to a radius of 115 kpc \citep{Moore06}.  Stellar disks are typically embedded in much larger \HI\ disks.  The size of the GLSB stellar disks is similar to the largest \HI\ disks observed in nearby galaxies, in support of the \citet{Mapelli08} model where the GLSB disks are the faded remnants of a normal \HI\ disk that has experienced a merger induced star-burst.

@@

In Figure~\ref{disk_comp}, we compare the sizes of the stellar disks of the GLSB galaxies with other observations.  For this plot, we take the maximum detected radius from the literature for the galaxies.  It is possible that deeper observations could increase the values of $R_{max}$.  While UGC 6614 is close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.  This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems without some additional source of angular momentum.

%/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.  Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1.  It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.  \label{disk_comp}}
\end{figure}

@@

The extracted rotation curves imply large dark matter halos.  For Malin 2, $V_{circ}\sim 280$ \kms at $R=42$ kpc implies a mass of $7.6\times 10^{11} \msun$ (compared to an SDSS stellar mass of $1.4\times 10^{11}$).  For UGC 6614, $V_{circ}\sim 200$ \kms at $R=17$ kpc gives a dynamical mass of $1.6\times 10^{11} \msun$ (compared to a stellar mass of$0.46\times 10^{11} \msun$ ).

@@

Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.  We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.  We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.  Each SFH can have a metallicity of [Z/H] = -2.3,-1.70,-0.70, -0.40, 0.0, or  0.40.  We do not include any metallicity evolution, as all the age bins in a given model has the same metallicity.  This gives us 361 unique non-zero model spectra.

@@

\begin{figure}
\epsscale{0.25}
\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps}
\plotone{Plots/databinned_Malin2.eps}\plotone{Plots/modelbinned_Malin2.eps}\plotone{Plots/data_modelbinned_Malin2.eps}
%\epsscale{.5}
\epsscale{1}
\plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
\caption{Fitting the line-of-sight velocity maps measured with Ppxf with the kinemetry package.  The dashed curve shows the expected stellar mass contribution to the rotation curve.  Vertical lines mark $R_e$ and $5R_e$.  \HI\ data from \citet{Pickering97}.  \label{malin_kinem}}
\end{figure}

@@

\begin{figure}
\epsscale{0.25}
\plotone{Plots/dataUGC06614.eps}\plotone{Plots/modelUGC06614.eps}\plotone{Plots/data_modelUGC06614.eps}
\plotone{Plots/databinned_UGC06614.eps}\plotone{Plots/modelbinned_UGC06614.eps}\plotone{Plots/data_modelbinned_UGC06614.eps}
%\epsscale{.5}
\epsscale{1}
\plottwo{Plots/kinembinned_UGC06614.eps}{Plots/kinem_HI_binned_UGC06614.eps}
\caption{Fitting the velocity maps with kinemetry package. Vertical lines mark $R_e$ and $5R_e$.  The dashed lines shows a rotation curve based in the enclosed flux, normalized so that all the SDSS stellar mass is contained within $3R_e$.  \HI\ data from \citet{Pickering97}.\label{ugc_kinem}}
\end{figure}

>>>>

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{xspace}
\def\arcsec{$^{\prime\prime}$}
\bibliographystyle{apj}
\newcommand\degree{{^\circ}}
\newcommand\surfb{$\mathrm{mag}/\square$\arcsec}
\newcommand\Gyr{\rm{~Gyr}}
\newcommand\msun{\rm{M}_\odot}
\newcommand\kms{km s$^{-1}$}
\newcommand\al{$\alpha$}
\newcommand\ha{$\rm{H}\alpha$}
\newcommand\hb{$\rm{H}\beta$}
\newcommand\HI{\ion{H}{1}}

@@

\citet{Galaz15} take deep images of Malin~1 and find the stellar disk extends to 160 kpc.

@@

\begin{deluxetable*}{l l c c c c c c}
%\tabletypesize{\small \footnotesize \scriptsize}
\tabletypesize{\small}
%\rotate
\tablewidth{0pt}
%\tablenum{num}
%\tablecolumns{num}
%\tableheadfrac{num}
\tablecaption{Basic Properties of GLSB Galaxies}
\tablehead{
\colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
& \colhead{$\sigma$} & Stellar Mass & \colhead{\HI\ mass}\\
     &  \colhead{(DR 9)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms}  &\colhead{log$_{10}$M$_{\odot}$}&\colhead{log$_{10}$M$_{\odot}$}
\label{basic_prop}}    
\startdata
XXX-add Malin 1
Malin 2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  & 11.15 & 10.6\\
UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 & 10.66 & 10.5
\enddata
\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS.}
\end{deluxetable*}

@@

The diameters of GLSB disks are very large, with Malin~1's stellar disk detected out to a radius of 115 kpc \citep{Moore06} and 80 kpc \citep{Galaz15}.  Stellar disks are typically embedded in much larger \HI\ disks.  The size of the GLSB stellar disks is similar to the largest \HI\ disks observed in nearby galaxies, in support of the \citet{Mapelli08} model where the GLSB disks are the faded remnants of a normal \HI\ disk that has experienced a merger induced star-burst.

@@

In Figure~\ref{disk_comp}, we compare the sizes of the stellar disks of the GLSB galaxies with other observations.  For this plot, we take the maximum detected radius from the literature for the galaxies.  It is possible that deeper observations could increase the values of $R_{max}$.  While UGC 6614 is close in size to the upper end of local \HI\ disks, Malin 1 and 2 are much larger than galaxies observed in the THINGS survey.  This seems to point against the GLSB formation mechanism of  \citet{Mapelli08}, as we do not observe \HI\ disks large enough to convert into GLSB systems unless an interaciton is able to boost the \HI\ angular momentum.

%/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Moore06}, Malin 2 and UGC 6614 from \citet{Pickering97}.  Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1 XXX.  It is interesting to note that the \emph{stellar} disks of GLSB galaxies can be larger than the \HI\ disks of nearby systems.  \label{disk_comp}}
\end{figure}

@@

The extracted rotation curves imply large dark matter halos.  For Malin 2, $V_{circ}\sim 280$ \kms at $R=42$ kpc implies a mass of $7.6\times 10^{11} \msun$ (compared to an SDSS stellar mass of $1.4\times 10^{11}$).  For UGC 6614, $V_{circ}\sim 200$ \kms at $R=17$ kpc gives a dynamical mass of $1.6\times 10^{11} \msun$ (compared to a stellar mass of $0.46\times 10^{11} \msun$ ).

@@

Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.  We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.  We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.  Each SFH can have a metallicity of [Z/H] = -2.3,-1.70,-0.70, -0.40, 0.0, or  0.40.  We do not include any metallicity evolution, as all the age bins in a given model has the same metallicity.  This gives us 361 unique non-zero model spectra. XXX-cite which SED code I'm using and IMF etc.

@@

\begin{figure*}
\epsscale{0.25}
\plotone{Plots/dataMalin2.eps}\plotone{Plots/modelMalin2.eps}\plotone{Plots/data_modelMalin2.eps} \\
\plotone{Plots/databinned_Malin2.eps}\plotone{Plots/modelbinned_Malin2.eps}\plotone{Plots/data_modelbinned_Malin2.eps}
%\epsscale{.5}
\epsscale{1}
\plottwo{Plots/kinembinned_Malin2.eps}{Plots/kinem_HI_binned_Malin2.eps}
\caption{Fitting the line-of-sight velocity maps measured with Ppxf with the kinemetry package.  The dashed curve shows the expected stellar mass contribution to the rotation curve.  Vertical lines mark $R_e$ and $5R_e$.  \HI\ data from \citet{Pickering97}.  \label{malin_kinem}}
\end{figure*}

@@

\begin{figure*}
\epsscale{0.25}
\plotone{Plots/dataUGC06614.eps}\plotone{Plots/modelUGC06614.eps}\plotone{Plots/data_modelUGC06614.eps} \\
\plotone{Plots/databinned_UGC06614.eps}\plotone{Plots/modelbinned_UGC06614.eps}\plotone{Plots/data_modelbinned_UGC06614.eps}
%\epsscale{.5}
\epsscale{1}
\plottwo{Plots/kinembinned_UGC06614.eps}{Plots/kinem_HI_binned_UGC06614.eps}
\caption{Fitting the velocity maps with kinemetry package. Vertical lines mark $R_e$ and $5R_e$.  The dashed lines shows a rotation curve based in the enclosed flux, normalized so that all the SDSS stellar mass is contained within $3R_e$.  \HI\ data from \citet{Pickering97}.\label{ugc_kinem}}
\end{figure*}
